My title

### 2024-02-14 outputs/paper/paper.qmd
graph done

# Data {#sec-data}
```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
sample_data <- head(bully_clean_data, 6)
data<-bully_clean_data
```

@@

```{r}
data$MonthIndicator <- factor(data$Month, levels = month.abb)

# Regression to remove seasonal patterns and time trends
pre_process_model <- lm(logSearchst ~ as.factor(Year) + MonthIndicator, data = data)
data$logSearchst_star <- residuals(pre_process_model)

# Step 2: Month-by-Month Event Study Model
event_study_model <- lm(logSearchst_star ~ factor(Month, ordered = TRUE) + alphaPriorYearst + factor(State), data = data)

# Step 3: Nationwide Before-After Specification
before_after_model <- lm(logSearchst_star ~ factor(PostCOVID) + factor(State), data = data)

# Step 4: Time Period Analysis
time_period_model <- lm(logSearchst_star ~ factor(PostSpring) + factor(PostSummer) + factor(PostFall) + factor(State), data = data)

# Step 5: Differential Impact Analysis
differential_model <- lm(logSearchst_star ~ factor(PostSpring) + factor(PostSummer) + factor(PostFall) + factor(PostFall) * InPersons + factor(State), data = data)

# Additional Information
# Clustered standard errors
library(lmtest)
coeftest(event_study_model, vcov. = vcovHC(event_study_model, type = "HC1"))

# Weighted by population
weighted_model <- lm(logSearchst_star ~ factor(Month, ordered = TRUE) + alphaPriorYearst + factor(State), data = data, weights = your_population_weights)
```

@@

```{r}
library(ggplot2)
library(dplyr)

# Assuming the date format is "%Y-%m-%d", you can use the following code
bully_data <- subset(bully_clean_data, bully_type == "bully")
bully_data <- bully_data %>%
  group_by(date) %>%
  summarise(Total = sum(num_of_searches))
schbully_data <- subset(bully_clean_data, bully_type == "schbully")
cyberbully_data <- subset(bully_clean_data, bully_type == "cyberbully")
# Create a ggplot object for the composite search measure
ggplot(bully_data, aes(x = date, y = Total)) +
  geom_point() +
  geom_segment(data = subset(bully_data, !is.na(lag(date))), aes(x = lag(date), y = lag(Total), xend = date, yend = Total), color = "blue") +
  ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
  xlab("Date") +
  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")

# Create a ggplot object for School Bullying search intensity
ggplot(schbully_data, aes(x = date, y = num_of_searches)) +
  geom_point() +
  geom_line() +
  ggtitle("Search Intensity for School Bullying") +
  xlab("Date") +
  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")

# Create a ggplot object for Cyberbullying search intensity
ggplot(cyberbully_data, aes(x = date, y = num_of_searches)) +
  geom_point() +
  geom_line() +
  ggtitle("Search Intensity for Cyberbullying") +
  xlab("Date") +
  ylab("Logarithm of Nationwide Search Intensity (Relative to Jan 2016)") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), linetype = "dashed", color = "red")
```

```{r}
data <- data.frame(
  x = c(1, 2, 3, 4, 5),
  y = c(2, 4, 1, 6, 3)
)

# 指定要连接的点
connections <- data.frame(
  x1 = c(1, 2, 3, 4),
  y1 = c(2, 4, 1, 6),
  x2 = c(2, 3, 4, 5),
  y2 = c(4, 1, 6, 3)
)

# 使用ggplot函数创建图形
ggplot(data, aes(x = x, y = y)) +
  geom_point(color = "blue", size = 3) +
  geom_segment(data = connections, aes(x = x1, y = y1, xend = x2, yend = y2), color = "red") +
  labs(title = "点连接不同点的图", x = "X轴", y = "Y轴") +
  theme_minimal()
```

>>>>

# Data {#sec-data}
```{r}
file_path <- "../../outputs/data/bully_clean_data.csv"
bully_clean_data <- read.csv(file_path)
bully_clean_data$date <- as.Date(bully_clean_data$date)
sample_data <- head(bully_clean_data, 6)
```

@@

@@

```{r}
library(ggplot2)
library(dplyr)
# Assuming the date format is "%Y-%m-%d", you can use the following code
bully_data <- subset(bully_clean_data, bully_type == "sch_cyb_bully")

bully_data <- bully_data %>%
  group_by(date) %>%
  summarise(Total = sum(num_of_searches))
schbully_data <- subset(bully_clean_data, bully_type == "schbully")
schbully_data <- schbully_data %>%
  group_by(date) %>%
  summarise(Total = sum(num_of_searches))
cyberbully_data <- subset(bully_clean_data, bully_type == "cyberbully")
cyberbully_data <- cyberbully_data %>%
  group_by(date) %>%
  summarise(Total = sum(num_of_searches))
# Create a ggplot object for the composite search measure
ggplot(bully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  ggtitle("Composite Search Intensity for School Bullying and Cyberbullying") +
  xlab("Date") +
  ylab("Search Intensity") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
   scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m-%d", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(schbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  ggtitle("Composite Search Intensity for School Bullying") +
  xlab("Date") +
  ylab("Search Intensity") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m-%d", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(cyberbully_data, aes(x = date),aes(y = Total),mapping = aes(x = date, y = Total, group = 1)) +geom_point()+
  geom_line() +
  ggtitle("Composite Search Intensity forCyberbullying") +
  xlab("Date") +
  ylab("Search Intensity") +
  geom_vline(xintercept = as.numeric(as.Date("2020-02-01")), 
             linetype = "dashed", color = "red")+
  scale_x_date(breaks = seq(as.Date("2012-01-01"), as.Date("2021-03-01"), by = "6 months"),
               date_labels = "%Y-%m-%d", 
               limits = c(as.Date("2012-01-01"), as.Date("2021-03-01")))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
